\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

%\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{xfrac}
\usepackage{mathabx}
\usepackage[UTF8]{ctex}
\usepackage{fontawesome}
\usepackage{xcolor}
\definecolor{longhorn}{rgb}{0.8, 0.33, 0.0}
\definecolor{airforceblue}{rgb}{0.1, 0.3, 0.6}
\usepackage[colorlinks = true,
            linkcolor = airforceblue,
            urlcolor  = airforceblue,
            citecolor = airforceblue,
            anchorcolor = airforceblue]{hyperref}

\newcommand{\MYhref}[3][airforceblue]{\href{#2}{\color{#1}{#3}}}%


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newcommand{\vvspace}{\vspace{0.1in}}



\begin{document}

\name{Luhao Zhang \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.7in}p{4in}}        
Department of Mathematics, PMA 8.100  & \faEnvelope  :  \MYhref{mailto:luhaozhang@math.utexas.edu}{luhaozhang@math.utexas.edu}\\         
 2515 Speedway Stop C1200 & \faHome : \MYhref{https://web.ma.utexas.edu/users/luhaozhang/}{web.ma.utexas.edu/users/luhaozhang/} \\       
  Austin, TX 78712-1202, USA & \faPhone : +1 (737) 270-5656 
\end{tabular}

%\vspace{-0.1in}

\section{\sc Research Area}
Stochastic and robust optimization, Data-driven decision-making under uncertainty, Machine learning

%\vspace{-0.1in}


\section{\sc Education}
{\bf The University of Texas at Austin}, Austin, TX, USA\\
\vspace*{-.15in}
\begin{list1}
\item[] \textbf{Ph.D. in Mathematics} \hfill Aug 2018 - May 2023
\item[] Advisor: \MYhref{https://web.ma.utexas.edu/users/zariphop/}{Thaleia Zariphopoulou}
\item[] Committee Member: \href{https://faculty.mccombs.utexas.edu/rui.gao/}{Rui Gao}, Irene M.~Gamba, Mihai Sirbu, Stathis Tompaidis
\end{list1}

{\bf Xi'an Jiaotong University}, Xi'an, Shaanxi, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.15in}
\begin{list1}
\item[] \textbf{B.S. in Mathematics and Applied Mathematics} (Honors Program) 
\hfill Aug 2014 - 2018
\end{list1}
\begin{itemize}
\setlength\itemsep{0.1em}
\item[] \href{https://en.wikipedia.org/wiki/Special_Class_for_the_Gifted_Young#Xi'an_Jiaotong_University}{\textit{Special Class for the Gifted Young}}
% : Early decision to the university after middle school 
% \item \textit{Full Scholarship} (1 out of 200) as a visiting student in \textbf{Columbia university} (Spring 2016) and \textbf{University of California, Berkeley} (Spring 2017)
\end{itemize}

\iffalse
{\bf Columbia University in the City of New York}, New York City, NY, USA\\
%{\em Department of Mathematics} 
\vspace*{-.15in}
\begin{list1}
\item[] Visiting Undergraduate Student \hfill Jan. - May 2016
\end{list1}

{\bf University of California, Berkeley}, Berkeley, CA, USA\\
%{\em Department of Mathematics} 
\vspace*{-.15in}
\begin{list1}
\item[]  Visiting Undergraduate Student \hfill Jan. - May 2017
\end{list1}

\fi


% {\bf University of Texas at Austin}, Austin, Texas USA\\
% %{\em Department of Mathematics} 
% \vspace*{-.1in}
% \begin{list1}
% \item[] Visiting Student Intern for Research Assistant \hfill Sept. - Dec. 2017 
% \end{list1}


%\vspace{-0.1in}



\section{\sc Research \\
Papers}
{\bf Publications}
%\vvspace
\begin{enumerate}[leftmargin=0.15in]
    \item Luhao Zhang, Jincheng Yang, Rui Gao. \textit{\MYhref{http://www.optimization-online.org/DB_HTML/2021/12/8749.html}{Optimal Robust Policy for Feature-Based Newsvendor}} (2022), \textit{\textbf{Management Science}}, forthcoming.
    \item Luhao Zhang, Mohsen Ghassemi, Ivan Brugere, Alan Mishle, Niccolo Dalmasso, Vamsi Potluru, Tucker Balch, Manuela Veloso. \textit{Conditional Demographic Parity Through Optimal Transport} (2022), NeurIPS Workshop on Algorithmic Fairness through the Lens of Causality and Privacy.
\end{enumerate}


% {\bf Under Revision}
% %\vvspace
% \begin{enumerate}[leftmargin=0.15in]
%     \setcounter{enumi}{1}
%     \item \textbf{Luhao Zhang}, Jincheng Yang, Rui Gao. \textit{\MYhref{https://arxiv.org/abs/2205.00362}{A Simple and General Duality Proof for Wasserstein Distributionally Robust Optimization}} (2022), under review for \textit{Management Science}, fast track.
% \end{enumerate}


% {\bf Conference Papers}
% \begin{enumerate}[leftmargin=0.15in]
% \setcounter{enumi}{2}
%     \item \textbf{Luhao Zhang}, Mohsen Ghassemi, Ivan Brugere, Alan Mishle, Niccolo Dalmasso, Vamsi Potluru. \textit{Conditional Demographic Parity Through Optimal Transport} (2022), NeurIPS Workshop on Algorithmic Fairness through the Lens of Causality and Privacy.
% \end{enumerate}

{\bf Preprints}
\begin{enumerate}[leftmargin=0.15in]
\setcounter{enumi}{2}
    \item Luhao Zhang, Jincheng Yang, Rui Gao. \textit{\MYhref{https://arxiv.org/abs/2205.00362}{A Simple and General Duality Proof for Wasserstein Distributionally Robust Optimization}} (2022), under review for \textbf{\textit{Management Science}} (fast track).
    \item Jincheng Yang*, Luhao Zhang*, Ningyuan Chen, Rui Gao, Ming Hu. \textit{\href{https://optimization-online.org/2022/10/decision-making-with-side-information-a-causal-transport-robust-approach/}{Decision-making with Side Information: A Causal Transport Robust Approach}} (2022), to be submitted to \textbf{\textit{Operations Research}}.
    \item Renyuan Xu*, Thaleia Zariphopoulou*, Luhao Zhang*. \textit{Decision Making with Learning and Opportunity to Reverse} (2022), to be submitted to \textbf{\textit{Operations Research}}.
    \item[] * indicates alphabetical order
\end{enumerate}



\section{\sc Industry Experience}
{\bf J.P.Morgan Chase, AI Research}, New York, NY
\vspace{-.3cm}

{\em AI Researcher (Intern)} \hfill { Jun - Aug 2022}
\begin{itemize}[leftmargin=0.15in]
\item Developed an efficient algorithm to achieve conditional demographic parity using causal transport distance
\item Preliminary result accepted by \textit{NeurIPS Workshop on Algorithmic Fairness through the Lens of Causality and Privacy}
\end{itemize}

% \section{\sc Technical Skills}
% {\bf Python, C++, }
% \vspace*{-.15in}

% {\em Optimal Policies for Robust Big Data Newsvendor} \hfill { May 2021}

% \section{\sc Award}


%\vspace{-.3cm}
\section{\sc Selected\\ 
Award}
Frank Gerth III Teaching Excellence Award, UT Austin \hfill {2021}

\vspace{-0.5cm}

Selected to present at the Cornell ORIE Young Researchers Workshop \hfill {2021}
%\vspace{-.3cm}

% \section{\sc Programming}
% Experience in Python, C++, R, Matlab, Mathematica

%\newpage




\section{\sc Invited Talks}
{\bf Optimal Robust Policy for Feature-Based Newsvendor}
\begin{itemize}[leftmargin=0.15in]
\item Robust Optimization Webinar Series  \hfill { May 2021}\\ 
\vspace{-0.2in}
\item International Conference of the Chinese Scholars Association for Management Science and Engineering (CSAMSE), Shanghai Jiaotong University \hfill{July 2021}

\item Cornell ORIE Young Researchers Workshop, Ithaca, NY \hfill{Oct 2021}

\item INFORMS Annual Meeting, Anaheim, CA \hfill{Oct 2021}

\item Conference on Artificial Intelligence, Machine Learning, and Business Analytics, Rutgers University \hfill{Dec 2021}
% \raggedleft Dec 2021 


% \raggedright

\item Texas Women in Math Symposium, Rice University \hfill{Feb 2022}

\item INFORMS Optimization Society Conference, Greenville, SC  \hfill{March 2022}
\end{itemize}

{\bf Decision Making with Learning and Opportunity to Reverse}

\begin{itemize}[leftmargin=0.15in]
\item SIAM Annual Meeting, Pittsburgh, PA \hfill{Jul 2022}
\item INFORMS Annual Meeting, Indianapolis, IN \hfill{Oct 2021}
\end{itemize}


\section{\sc Teaching experience}
{\bf UT Austin, Teaching Assistant}
\vspace{-0.3cm}

% \underline{Statistics and Applied Mathematics}
\vvspace
\begin{itemize}[leftmargin=0.15in]
\item M378K \textit{Introduction to Mathematical Statistics} \quad 4.0/5.0  \hfill {Spring, Fall 2022}
\item M408K \textit{Differential Calculus} \quad 4.5/5.0 \hfill {Spring 2021}
\item M358K \textit{Applied Statistics} \quad 4.0/5.0 \hfill {Fall 2021}
\item M362K \textit{Probability} \quad 4.3/5.0  \hfill { Fall 2020}
% \vspace{-0.2in}

% \end{itemize}

% % \underline{Pure Mathematics}
% % \vvspace
% \begin{itemize}[leftmargin=0.15in]

\item MF325K \textit{Discrete Mathematics} \quad 4.3/5.0  \hfill { Summer 2020}
% \vspace{-0.2in}
\item M427L \textit{Advanced Calculus for Applications II} \quad 4.1/5.0 \hfill{Spring 2020}
\item M348 \textit{Scientific Computation in Numerical Analysis} \quad N/A \hfill{Spring, Fall 2019}
\item M408D \textit{Sequences, Series, and Multivariable Calculus} \quad 4.2/5.0 \hfill{Fall 2018}
\end{itemize}


% \section{\sc Conferences \& Workshops Attended}
% \begin{itemize}[leftmargin=0.15in]
% \item Decision Making in Health and Medical Care, IMSI \hfill { May 2021}
% \item SIAM Conference on Financial Mathematics and Engineering  \hfill { June 2021}\\
% \vspace{-0.2in}
% \item SIAM Conference on Control and Its Applications \hfill{July 2021}
% \item  SIAM Annual Meeting \hfill{July 2021}
% \item SIAM Conference on Optimization \hfill{July 2021}
% \item 6th Berlin Workshop for Young Researchers on Mathematical Finance \hfill{Aug 2021}
% \item Decision Making and Uncertainty, IMSI \hfill{Mar - May 2022}
% \end{itemize}

\section{\sc Professional Services}
{\bf Referee}
\vvspace
\begin{itemize}[leftmargin=0.15in]
\item Mathematical Programming 
\item ACM International Conference on AI in Finance
\end{itemize}
{\bf Session Chair}
\begin{itemize}[leftmargin=0.15in]
    \item INFORMS 2021 invited session of Learning and Decision-making with Contextual Information
    \item INFORMS 2022 invited session of Data-driven Decision Making
\end{itemize}



\section{\sc Outreach}
{\bf \href{https://web.ma.utexas.edu/users/drp/about.html}{Directed Reading Program} Mentor}
\vvspace
\begin{itemize}[leftmargin=0.15in]
\item Sonali Singh, on the topic of \textit{Stochastic Calculus for Finance} \hfill {Spring 2020}
\item Wenxuan Jiang, on the topic of \textit{Stochastic Calculus for Finance} \hfill {Fall 2021}
\item Haoze Yan, on the topic of \textit{Lectures on Stochastic Programming} \hfill {Spring, Fall 2022}
\item Yuxiang Gao, on the topic of \textit{Elements of Statistical Learning} \hfill {Spring 2022}
\end{itemize}


\section{\sc References}
\begin{minipage}[t]{0.8\textwidth}
  \textbf{Rui Gao}\\
  Department of Information, Risk, and Operations Management\\
  The University of Texas at Austin\\
  E-mail: \href{mailto: rui.gao@mccombs.utexas.edu}{ rui.gao@mccombs.utexas.edu}
\end{minipage}

% \hfill
\begin{minipage}[t]{0.8\textwidth}
  \textbf{Renyuan Xu}\\
  Epstein Department of Industrial and Systems Engineering\\
  University of Southern California\\
  E-mail: \href{mailto: renyuanx@usc.edu}{ renyuanx@usc.edu}
\end{minipage}


\begin{minipage}[t]{0.8\textwidth}
  \textbf{Thaleia Zariphopoulou}\\
  Department of Mathematics\\
  The University of Texas at Austin\\
  E-mail: \href{mailto:zariphop@math.utexas.edu}{zariphop@math.utexas.edu}
\end{minipage}

% \section{\sc Programming}
% Python (Scikit-Learn, TensorFlow, SciPy, Gurobi, Mosek), C++, R, Matlab, Mathematica

% \section{\sc Research Topics}
% \begin{itemize}[leftmargin=0.15in]
% \item Robust portfolio selection
% \item Markets with frictions
% \item Partial information
% \item Rational inattention
% \item Nonlinear filtering
% \item Information costs
% \end{itemize}




\iffalse
\section{\sc Professional Employment}
{\bf China International Capital Corporation (Henan)}, Zhengzhou, China
\vspace{-.3cm}

{\em Private Equity Analyst (Intern)} \hfill {\bf Dec. 2017 - Feb. 2018}\\
% \begin{list2}
% \item Conducted commercial due diligence and comparable companies analysis in an pre-IPO investment deal of a power battery company
% \item Performed industry and firm specific research on an electric logistics car company
% \item Implemented industry research on China’s PE/VC market and governmental investment funds 
% \end{list2}

{\bf Chinese Academy of Sciences}, Beijing, China
\vspace{-.3cm}

{\em Research Assitant} \hfill {\bf July - Sept. 2017, July - Sept. 2016}\\
{\em National Undergraduate Student Innovation Program} (fellowship funded) \\
{\em Visting Researcher for the State Key Laboratory of Scientific and Engineering Computing (LSEC)}
\smallskip
% \begin{list2}
% \item Topics:  Model for ranking personal credit (in practice)
% \item Advisor: Yuhong Dai,  Feng Kang Chair Professor  
% \item  Statistical Model Selection, Factor Selecting
% \end{list2}

{\bf Peking University}, Beijing, China
\vspace{-.3cm}

{\em Research Assitant} \hfill {\bf July 2016 - Sept. 2016}\\
% \begin{list2}
% \item Topics: Conception, development and implementation on the illiquidity in stock returns
% \item Advisor: Yao Wang
% \item Sparse Evolutive models, Multiscale Representations
% \end{list2}


\section{\sc Academic Experience}

{\bf University of Texas at Austin}, Austin, Texas USA
\vspace{-.3cm}

{\em Research Intern} \hfill {\bf Sept - Dec. 2017}\\
\begin{list2}
\item Topics: Several inverse problems in partial differential equations
\item Advisor: Kui Ren. 
\item Scattering Representations of Stochastic Processes
\end{list2}




{\bf University of California, Berkeley}, Berkeley, California USA

\vspace{-.3cm}
{\em Research Trainee} \hfill {\bf Mar. 2017 - June 2017}\\
\begin{list2}
\item Topics: Stochastic model reduction by NARMA Model
\item Advisor: Fei Lu
\item Stochastic Differential Equations
\end{list2}



{\bf Xi'an Jiaotong University}, Xi'an,  Shaanxi China

\vspace{-.3cm}
{\em Research Trainee} \hfill {\bf July. 2017 - Present}\\
\begin{list2}
\item Topics: Dynamic behaviour of FitzHugh-Nagumo model
\item Advisor: Yanmei Kang
\item Internal Noise, Spatial Coherence Resonance
\end{list2}


{\em Research Trainee} \hfill {\bf Sept. 2016 - Dec. 2016}\\
\begin{list2}
\item Topics: Identified of risk schizophrenia-associated loci with PCI method
\item Advisor: Chen Qiao
\item Feature Back-selection Method, Space Saving Ability, Accuracy Rate
\end{list2}


\section{\sc Papers} 
\begin{list1}
\item[] Qiao C., Sun K., Zhang L. \& Zhang W. \textit{Feature selection method by DL on handwritten digits datasets}, in preparation.
\end{list1}

\section{\sc Awards and Patents} 
\begin{list2}
\item Certificate of Utility Model Patent: ZL 2013 2 0431220.0. \hfill { Jan. 2014}

\begin{list1}
\item[] This patent consists of a new design for cradles with adjustable supporting area according to the growth of babies. 
\end{list1}

\item Honorable Mention Prize in 2015 Interdisciplinary Contest in Modeling. \hfill { Feb. 2015}

\item Honorable Mention Prize in 2017 Interdisciplinary Contest in Modeling. \hfill { Feb. 2017}
\end{list2}


\section{\sc Computer Skills} 
\begin{list2}
\item Math-related:  Matlab, Mathematica, R, \LaTeX.
\item Programming:  C++.
\end{list2}

\section{\sc Standardized Tests}
\begin{list1}
\item[] TOEFL: 95  (R:27, L:24, S:19, W:25) 
\item[] IELTS: 7  (R:8, L:7, S:6, W:6) 
\item[] GRE: 324 (V:156, Q:168)
\end{list1}
\fi

\end{resume}
\end{document}